Death By Dropdown?

### 2025-04-01 conference-materials/2025_shiny-conf/slides.qmd
Updates slide titles and formats for consistency
- Revises slide titles for uniformity across code example slides.
- Cleans up and formats code within slides for better readability.
- Adjusts text and animations on slide 17 to enhance presentation flow.

::: {.notes}
**Case Study Introduction (1-1.5 min):**

@@

::: {.notes}
**Visual Impact**: Connect code to visual results.

- "Here's what our reactable implementation looks like in practice"
- For each image as it appears:
  * First image: "Notice how the grouped bars implement Stage 1 principles by reducing cognitive load"
  * Second image: "The dynamic legend addresses Hick's Law by simplifying choices"
  * Third image: "Color coding enhances processing fluency from Stage 2"
  * Fourth image: "The grouping clearly implements the Principle of Proximity from Stage 3"
- "Each of these visual elements directly ties to a principle from the BID framework"
- "This is the power of intentional design - every element has a psychological purpose"
- Transition: "Now let's look at our final reactable example with team collaboration features..."
:::

## Implementation Demo: {reactable} Basics {background-color="#f9f9f9"}

::: {.r-fit-text}
Using `{reactable}` to implement Stages 1-3
:::

@@

  # Stage 2: Processing Fluency - Color coding for instant insights
  columns = list(
    Metric1 = colDef(
      style = function(value) {
        # Color coding enhances processing fluency
        if (value > 50) {
          list(background = "rgba(0, 128, 128, 0.2)", 
               color = "#006666", fontWeight = "bold")
        } else if (value < 30) {
          list(background = "rgba(255, 140, 0, 0.2)", 
               color = "#dd8500", fontWeight = "bold")
        }
      }
    )
  )
)
```

@@

## Implementation Demo: {reactable} Advanced {background-color="#f9f9f9"}

::: {.r-fit-text}
Enhanced Implementation with Bar Charts, Grouping, and Progressive Disclosure
:::

```r
reactable(
  soundpulse_data,
  # Stage 3: Principle of Proximity - Group related elements visually
  columnGroups = list(
    colGroup(name = "System 1 - Quick Insights", 
             columns = c("Metric1", "Metric2")),
    colGroup(name = "System 2 - Detailed Analysis", 
             columns = c("Metric3", "Metric4"))
  ),

@@

  # Progressive disclosure supports Cognitive Load Theory
  details = function(index) {
    # Only show details when requested
    detailed_data <- segment_details[segment_details$claim_id == 
                                     soundpulse_data$Claim[index], ]
    div(
      style = "padding: 1rem",
      reactable(detailed_data, outlined = TRUE, striped = TRUE)
    )
  }
)
```

@@

::: {.r-fit-text}
Complete Dashboard with Multiple BID Principles
:::

@@

## Implementation Demo: {echarts4r} Basics {background-color="#f9f9f9"}

::: {.r-fit-text}
Using `{echarts4r}` to implement Stages 4-5
:::

@@

## Implementation Demo: {echarts4r} Reference Lines {background-color="#f9f9f9"}

::: {.r-fit-text}
Adding Benchmark References to Address Anchoring Effect
:::

@@

## Implementation Demo: {echarts4r} Framing Toggle {background-color="#f9f9f9"}

::: {.r-fit-text}
Implementing Framing & Loss Aversion Principles with Interactive Toggle
:::

@@

## Interactive Demonstration: Framing Effect {background-color="#e6f0ff"}

### How Framing Affects Perception & Decision-Making

:::: {.columns .nonincremental}
::: {.column width="50%" .fragment}
#### Progress Framing:
<!-- going to change these screenshots to be more focused on a single bar -->
![](img/progress-frame.png){width="90%"}

- Motivates by highlighting achievement
- Creates positive momentum
- Supports incremental improvement
:::

::: {.column width="50%" .fragment}
#### Gap Framing:
<!-- going to change these screenshots to be more focused on a single bar -->
![](img/gap-frame.png){width="90%"}

- Creates urgency to address shortfall
- Highlights areas needing improvement
- May trigger risk-avoidance behaviors
:::
::::

>>>>

::: {.notes}
**Case Study Introduction:**

@@

::: {.notes}
**Visual Impact**: Connect UI to stages/concepts just mentioned.

- "Here's what our reactable implementation looks like in practice"
- For each image as it appears:
  * First image: "Notice how the grouped bars implement Stage 1 principles by reducing cognitive load"
  * Second image: "The dynamic legend addresses Hick's Law by simplifying choices"
  * Third image: "Color coding enhances processing fluency from Stage 2"
  * Fourth image: "The grouping clearly implements the Principle of Proximity from Stage 3"
- "Each of these visual elements directly ties to a principle from the BID framework"
- "This is the power of intentional design - every element has a psychological purpose"
:::

## {reactable} Implementation: Basics {background-color="#f9f9f9"}

@@

  # Stage 2: Processing Fluency - Color coding for instant insights
  columns = list(
    Metric1 = colDef(
      style = function(value) {
        # Color coding enhances processing fluency
        if (value > 50) {
          list(
            background = "rgba(0, 128, 128, 0.2)", 
            color = "#006666",
            fontWeight = "bold"
          )
        } else if (value < 30) {
          list(
            background = "rgba(255, 140, 0, 0.2)", 
            color = "#dd8500",
            fontWeight = "bold"
          )
        }
      }
    )
  )
)
```

@@

## {reactable} Implementation: Advanced {background-color="#f9f9f9"}

```r
reactable(
  soundpulse_data,
  # Stage 3: Principle of Proximity - Group related elements visually
  columnGroups = list(
    colGroup(
      name = "System 1 - Quick Insights", 
      columns = c("Metric1", "Metric2")
    ),
    colGroup(
      name = "System 2 - Detailed Analysis", 
      columns = c("Metric3", "Metric4")
    )
  ),

@@

  # Progressive disclosure supports Cognitive Load Theory
  details = function(index) {
    # Only show details when requested
    detailed_data <- segment_details[
      segment_details$claim_id == soundpulse_data$Claim[index], 
    ]
    div(
      style = "padding: 1rem",
      reactable(detailed_data, outlined = TRUE, striped = TRUE)
    )
  }
)
```

@@

@@

## {echarts4r} Implementation: Gauge Chart {background-color="#f9f9f9"}

@@

## {echarts4r} Implementation: Context {background-color="#f9f9f9"}

@@

## {echarts4r} Implementation: Framing {background-color="#f9f9f9"}

@@

## How Framing Affects Decision Making {background-color="#e6f0ff"}

::: {.column .r-fit-text .fragment}
![](img/progress-frame.png){width="90%"}

::: {.nonincremental}
- **Progress (gain) Framing:**
  * Motivates by highlighting achievement
  * Creates positive momentum
  * Supports incremental improvement
:::
:::

::: {.column .r-fit-text .fragment}
![](img/gap-frame.png){width="90%"}

::: {.nonincremental}
- **Gap (loss) Framing:**
  * Creates urgency to address shortfall
  * Highlights areas needing improvement
  * May trigger risk-avoidance behaviors
:::
:::
